New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2022-09-07 paper/paper.Rmd
Software before application.
Re-doing mathematica plots from the new notebooks, to match videos

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.32\textwidth]{figures/proj1_rf.png}
\includegraphics[width=0.32\textwidth]{figures/proj1_lda.png}
\includegraphics[width=0.32\textwidth]{figures/proj1_data.png}}
\caption{Projection identified using the manual tour, because it reveals an interesting structure in the predictions from the RF model (left). We can clearly see a block structure, while the LDA model (middle) produces linear boundaries. The three groups are nicely separated in this projection of the data (right)}.
\label{proj1}
\end{figure*}

@@

>>>>

@@

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.32\textwidth]{figures/proj1_rf.png}
\includegraphics[width=0.32\textwidth]{figures/proj1_lda.png}
\includegraphics[width=0.32\textwidth]{figures/proj1_data.png}}
\caption{Projection identified using the manual tour, because it reveals an interesting structure in the predictions from the RF model (left). We can clearly see a block structure, while the LDA model (middle) produces linear boundaries. The three groups are nicely separated in this projection of the data (right).}
\label{proj1}
\end{figure*}

This example can be reproduced with the code in penguins_exploring_manually.nb and a run through is shown in the video at (post to vimeo, same name as the nb).

This example can be reproduced with the code in penguins_slicing_through_center.nb and a run through is shown in the video at (post to vimeo, same name as the nb).

This example can be reproduced with the code in penguins_shifting_slice_center.nb and a run through is shown in the video at (post to vimeo, same name as the nb but one for positive and one for negative shift).

### 2022-09-07 paper/paper.tex
Re-doing mathematica plots from the new notebooks, to match videos

>>>>

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.32\textwidth]{figures/proj1_rf.png}
\includegraphics[width=0.32\textwidth]{figures/proj1_lda.png}
\includegraphics[width=0.32\textwidth]{figures/proj1_data.png}}
\caption{Projection identified using the manual tour, because it reveals an interesting structure in the predictions from the RF model (left). We can clearly see a block structure, while the LDA model (middle) produces linear boundaries. The three groups are nicely separated in this projection of the data (right).}
\label{proj1}
\end{figure*}

This example can be reproduced with the code in
penguins\_exploring\_manually.nb and a run through is shown in the video
at (post to vimeo, same name as the nb).

This example can be reproduced with the code in
penguins\_slicing\_through\_center.nb and a run through is shown in the
video at (post to vimeo, same name as the nb).

This example can be reproduced with the code in
penguins\_shifting\_slice\_center.nb and a run through is shown in the
video at (post to vimeo, same name as the nb but one for positive and
one for negative shift).
